API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Typo punctuation
Consistency

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of input/output
values $([x_1,..., x_p]^\mathrm{T}, y)$. of these variables. A widely used
representation of a dataset, a collection of
such samples, is a set of two matrix of numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of input/output
values $([x_1,..., x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrix with numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.
